### 2018-05-07 manuscript/data.tex

>>>>

In the report (looking for some report), the penetration of mobile device is XXX, almost every XX people got a Mobile Phone in the urban. XX. As Figure~\ref{fig:data_over} shows, multiple social characteristics of a people is sampled, including income, education, etc.

\begin{figure}[htb!]
 \centering % avoid the use of \begin{center}...\end{center} and use \centering instead (more compact)
 \includegraphics[width=\columnwidth]{pictures/data_over1}
 \caption{Overview of Social Characteristics}
 \label{fig:data_over}
\end{figure}

The coverage of the data in spatial and social aspects. The distribution of age is consistent to the traditional survey (Shenzhen Census?).... Figure~\ref{fig:data_stat} shows...

\begin{figure}[htb!]
 \centering % avoid the use of \begin{center}...\end{center} and use \centering instead (more compact)
 \includegraphics[width=\columnwidth]{pictures/data_detail}
 \caption{Statistics}
 \label{fig:data_stat}
\end{figure}

### 2018-05-07 manuscript/visualdesign.tex

>>>>

\subsection{Data-driven Profile Design}

Figure~\ref{fig:design_profile} shows the legend for the user profile. Those design dimensions are driven by data. an intuitive perception of the social characteristics.

\begin{figure}[htb!]
 \centering % avoid the use of \begin{center}...\end{center} and use \centering instead (more compact)
 \includegraphics[width=\columnwidth]{pictures/design_profile}
 \caption{Design Profile}
 \label{fig:design_profile}
\end{figure}

Various profiles are generated. Figure~\ref{fig:div_profile} shows some results.

\begin{figure}[htb!]
 \centering % avoid the use of \begin{center}...\end{center} and use \centering instead (more compact)
 \includegraphics[width=\columnwidth]{pictures/design_div}
 \caption{Diverse Profile}
 \label{fig:div_profile}
\end{figure}

\subsection{Interactive Group Classification}

Figure~\ref{fig:mds} is the MDS project of diversse users. Contour detected. Classification Updated. Automatic ensembling of diverse profiles.

\begin{figure}[htb!]
 \centering % avoid the use of \begin{center}...\end{center} and use \centering instead (more compact)
 \includegraphics[width=\columnwidth]{pictures/mds}
 \caption{Interactive Labelling and Classification}
 \label{fig:mds}
\end{figure}
